Time Prints of New Physics at Neutrino Telescopes

### 2024-01-05 paper/sections/introduction.tex

On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}, but also in testing temporal correlation of MeV neutrino events with fast radio bursts with its precise timing measurements \cite{IceCube:2019acm}. In this work, we demonstrate that such timing measurements will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles. This novel timing patterns generically exist in models with new weakly interacting particles, such as sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}, Majoron models \cite{Fiorillo:2022cdq}. Once produced inside the SN, these particles stream out at an earlier time than the standard neutrino signal. Meanwhile, for non-negligible mass, these particle would travel slower than active neutrino before decaying or converting back to active neutrinos. Via the timing measurement, we will show that neutrino telescope can provide unprecedented constraints on the parameter space in BSM.\\

>>>>

On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der},but also in testing temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm} by detecting a collective rise in all photomultiplier rates within a time window as short as 0.01 second on the top of the background noise. In this work, we demonstrate that such precise time resolutions will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles. This novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron models \cite{Fiorillo:2022cdq}, sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}. Once produced inside the SN, these particles stream out at an earlier time than the standard neutrino signal. Meanwhile, for non-negligible mass, they would travel slower than active neutrino before decaying or converting back to active neutrinos. Via the timing measurement, we will show that neutrino telescope can provide unprecedented constraints on the parameter space in BSM.\\

### 2024-01-05 paper/sections/model.tex

Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit. The results are in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out. Along its way towards the Earth, Majorons will decay to active neutrinos. For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
\begin{align}
    \Delta t = L_1/\beta + D_{\rm SN} \cos\theta-L_1 \cos\alpha -D_{\rm SN}\,,
    \label{eq:deltat}
\end{align}
with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.
The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$. As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}. For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different time. 
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
    Jeff needs to write here. {\color{red} Also, as for 1MeV case, the limit is set by the flux between 0.01s -0.1s, shall we choose t = 0.05s as one benchmark time in this plot? we can choose t = 0.05, 0.1, 0.5, 1, 5. Also I forgot why I can only see four lines here for each color?}
    }
    \label{fig:fluxes}
\end{figure}
{\color{red} Yingying will add some discussions about the updated flux plot.}

>>>>

Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit, which is in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out. Along its way towards the Earth, Majorons will decay to active neutrinos. For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
\begin{align}
    \Delta t = L_1/\beta + D_{\rm SN} \cos\theta-L_1 \cos\alpha -D_{\rm SN}\,,
    \label{eq:deltat}
\end{align}
with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.

The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$. As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}. For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different times for two benchmarks 
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
    Jeff needs to write here.
    }
    \label{fig:fluxes}
\end{figure}
